Environments and eval in R

### 2020-12-22 analysis/environments.Rmd
Decompose environment class

---
title: "Environments and eval in R"
author: "Pierre Donat-Bouillud"
output:
  html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: /var/lib/R/project-evalR
  calls_packages_path: /run/package-evals-traced.10/summarized-packages.fst
---

@@

source("insights.R", local = knitr::knit_global())
```

@@

eval_calls <- read_fst(eval_calls_path) %>%
  as_tibble()
```

@@

>>>>

---
title: "Environments and eval in R"
author: "Pierre Donat-Bouillud"
output:
  html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data
  calls_packages_path: /package/summarized.fst
---

@@

source("inc/insights.R", local = knitr::knit_global())
```

@@

eval_calls <- read_fst(eval_calls_path) %>%
  as_tibble()

stopifnot(!is.na(eval_calls$eval_call_srcref))
```

@@

Now, we can further decompose the environment class to get more insights. It has three components:

- how many times it has been wrapped in `new`
- how far (in terms of hierarchy of environments) it is from the callee
- does it correspond to any distinguished environment? ( `global`, `empty`, `base`, `callee`, or some package environment

```{r}
# new+new+new+new+caller-2-global
# str_match("caller-2-", "((?:new\\+)*)caller-([[:digit:]]+)-(.*)")

env_calls <- eval_calls_absolute %>%
  extract(environment_class, regex = "((?:new\\+)*)caller-([[:digit:]]+)-(.*)", into = c("new_env", "hierarchy", "specific_env"), remove = FALSE, convert = TRUE) %>%
  mutate(new_env = na_if(new_env, ""), specific_env = na_if(specific_env, ""), new_env = str_count(new_env, fixed("new+"))) %>%
  mutate(specific_env = if_else(specific_env == "emptyR_EmptyEnv", "empty", specific_env))
```
